---
title: "hw2"
author: "chenbo"
date: "2021/9/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Data Cleaning

Read in the data(the data is already on the desktop so I can read it directly)
```{r}
data<-read.csv("best_singles.csv")
#take a look at the data
head(data)
```
See if there is any missing value
```{r}
sum(is.na(data))
```
So there is no missing value, the data is good.

## Make a summary table of the time they used. 
```{r}
timetable<-summary(data$time)
timetable
```
So the fastest time is 3.47 seconds and the slowest is 7.18 seconds. And the mean time is 6.424 seconds.

## Make a plot to see how the time changes as the rank goes up and if there is any outlier
```{r}
plot(data$rank, data$time, xlab="rank", ylab="time/s", main = "Plot of Time and Rank")
```
The plot looks very smooth, only the first point is a little away from the others, which means the time he used is a lot faster than the others.
